Summary Tables

### 2019-05-17 summary_tables.Rmd

for(city in cities){
  df <- io[[city]]$trip_scen_sets
  u_trips <- df %>% dplyr::filter(scenario == "Baseline") %>% summarise(uid <- n_distinct(trip_id)) %>% as.numeric()
  td <- df %>% distinct(trip_id, scenario, .keep_all = T) %>% group_by(trip_mode, scenario) %>% summarise(p = round(dplyr::n() / u_trips * 100, 1)) %>% spread(key = trip_mode, value = p) %>% mutate(row_sums = rowSums(.[sapply(., is.numeric)], na.rm = TRUE))
  td <- as.data.frame(t(td))
  names(td) <- lapply(append('baseline', rownames(scen_prop)), as.character)
  td <- td[-1, ]
  x <- match(row.names(td), trip_order$mode)
  x[!is.na(x)]
  td <- td[order(x),]
  print(kable(td, caption = paste("Trip proportion (%) by mode for ", city)))
  cat("\n")
}

@@

for(city in cities){
  count_people <- nrow(io[[city]]$synth_pop)
  td <- io[[city]]$dist %>% filter(stage_mode != 'bus_driver') %>% mutate_if(is.numeric, round, digits = round_to) %>% mutate_if(is.numeric, list(~round((.) / count_people, round_to)))
  colnames(td)[3:7] <- rownames(scen_prop)
  x <- match(td$stage_mode, trip_order$mode)
  x[!is.na(x)]
  td <- td[order(x),]
  print(kable(td, caption = paste("Distance table (km) for ", city, "( ", count_people, " ) per person")))
  cat("\n")

  count_people <- length(unique(io[[city]]$trip_scen_sets$participant_id))
  td <- io[[city]]$dist %>% filter(stage_mode != 'bus_driver') %>% mutate_if(is.numeric, round, digits = round_to) %>% mutate_if(is.numeric, list(~round((.) / count_people, round_to)))
  colnames(td)[3:7] <- rownames(scen_prop)
  x <- match(td$stage_mode, trip_order$mode)
  x[!is.na(x)]
  td <- td[order(x),]

@@

for(city in cities){
  count_people <- nrow(io[[city]]$synth_pop)
  td <- io[[city]]$dur %>% filter(stage_mode != 'bus_driver') %>% mutate_if(is.numeric, round, digits = round_to) %>% mutate_if(is.numeric, list(~round((.) / count_people, round_to)))
  colnames(td)[3:7] <- rownames(scen_prop)
  x <- match(td$stage_mode, trip_order$mode)
  x[!is.na(x)]
  td <- td[order(x),]
  print(kable(td, caption = paste("Duration table (mins) for ", city, "( ", count_people, " ) per person (everyone)")))

  count_people <- length(unique(io[[city]]$trip_scen_sets$participant_id))
  td <- io[[city]]$dur %>% filter(stage_mode != 'bus_driver') %>% mutate_if(is.numeric, round, digits = round_to) %>% mutate_if(is.numeric, list(~round((.) / count_people, round_to)))
  colnames(td)[3:7] <- rownames(scen_prop)
  x <- match(td$stage_mode, trip_order$mode)
  x[!is.na(x)]
  td <- td[order(x),]
  print(kable(td, caption = paste("Duration table (mins) for ", city, "( ", count_people, " ) per person (people with trips)")))
  cat("\n")
}

>>>>

for(city in cities){
  df <- io[[city]]$trip_scen_sets
  u_trips <- df %>% dplyr::filter(scenario == "Baseline") %>% summarise(uid <- n_distinct(trip_id)) %>% as.numeric()
  td <- df %>% distinct(trip_id, scenario, .keep_all = T) %>% group_by(trip_mode, scenario) %>% summarise(p = round(dplyr::n() / u_trips * 100, 1)) %>% spread(key = trip_mode, value = p) %>% mutate(row_sums = rowSums(.[sapply(., is.numeric)], na.rm = TRUE))
  td <- as.data.frame(t(td))
  names(td) <- lapply(append('baseline', rownames(scen_prop)), as.character)
  td <- td[-1, ]
  x <- match(row.names(td), trip_order$mode)
  x[!is.na(x)]
  td <- td[order(x),]

  print(kable(td, caption = paste("Trip proportion (%) by mode for ", city)))
  cat("\n")
}

@@

for(city in cities){
  count_people <- nrow(io[[city]]$synth_pop)
  td <- io[[city]]$dist %>% filter(stage_mode != 'bus_driver') %>% mutate_if(is.numeric, round, digits = round_to) %>% mutate_if(is.numeric, list(~round((.) / count_people, round_to)))
  colnames(td)[3:7] <- rownames(scen_prop)

  x <- match(td$stage_mode, trip_order$mode)
  x[!is.na(x)]
  td <- td[order(x),]
  row.names(td) <- NULL

  print(kable(td, caption = paste("Distance table (km) for ", city, "( ", count_people, " ) per person")))
  cat("\n")

  count_people <- length(unique(io[[city]]$trip_scen_sets$participant_id))
  td <- io[[city]]$dist %>% filter(stage_mode != 'bus_driver') %>% mutate_if(is.numeric, round, digits = round_to) %>% mutate_if(is.numeric, list(~round((.) / count_people, round_to)))
  colnames(td)[3:7] <- rownames(scen_prop)
  x <- match(td$stage_mode, trip_order$mode)
  x[!is.na(x)]
  td <- td[order(x),]
  row.names(td) <- NULL

@@

for(city in cities){
  count_people <- nrow(io[[city]]$synth_pop)
  td <- io[[city]]$dur %>% filter(stage_mode != 'bus_driver') %>% mutate_if(is.numeric, round, digits = round_to) %>% mutate_if(is.numeric, list(~round((.) / count_people, round_to)))
  colnames(td)[3:7] <- rownames(scen_prop)

  x <- match(td$stage_mode, trip_order$mode)
  x[!is.na(x)]
  td <- td[order(x),]
  row.names(td) <- NULL

  print(kable(td, caption = paste("Duration table (mins) for ", city, "( ", count_people, " ) per person (everyone)")))

  count_people <- length(unique(io[[city]]$trip_scen_sets$participant_id))
  td <- io[[city]]$dur %>% filter(stage_mode != 'bus_driver') %>% mutate_if(is.numeric, round, digits = round_to) %>% mutate_if(is.numeric, list(~round((.) / count_people, round_to)))
  colnames(td)[3:7] <- rownames(scen_prop)

  x <- match(td$stage_mode, trip_order$mode)
  x[!is.na(x)]
  td <- td[order(x),]
  row.names(td) <- NULL

  print(kable(td, caption = paste("Duration table (mins) for ", city, "( ", count_people, " ) per person (people with trips)")))
  cat("\n")
}
